---
title: "Thesis Code"
author: "Nicholas Johnson"
date: "2025-01-23"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages
```{r}
library(tidyverse)
library(tibble)
library(MASS)
library(ordinal)
library(pscl)
library(nnet)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggeffects)
library(car)
library(effects)
library(officer)
library(flextable)
library(nnet)
library(broom)
library(knitr)
```


## Reorganize NJ1-3 to be 2 rows: frame and value, using pivot longer/wider. 
```{r}
load("C:/Users/nickj/OneDrive/Desktop/Thesis2025/NJ_Omnibus_1 (1).rdata")
data <- NJ_Omnibus_1
x <- pivot_longer(data, cols = c(NJ1, NJ2, NJ3),
               names_to = "Frame",
               values_to = "Importance",
               values_drop_na = TRUE)
```

## Convert all necessary responses to their corresponding type (character/factor)
```{r}

x$Frame <- as.factor(x$Frame)
x$Frame <- relevel(x$Frame, ref = "NJ3")
```



## Organizing Data for Ordinal Regression
```{r}
## Reclassifying variables
x$NJ6 <- as.factor(x$NJ6)
x$NJ11 <- as.factor(x$NJ11)
x$racethn <- as.factor(x$racethn)
x$sex <- as.factor(x$sex)
x$D5 <- as.numeric(x$D5)
x$D8 <- as.factor(x$D8)
x$D1 <- as.factor(x$D1)
x$Importance <- factor(x$Importance, ordered = T)
x$NJ4 <- factor(x$NJ4, ordered = T)
x$NJ5 <- factor(x$NJ5, ordered = T)
```

## Running an Ordinal Model to Predict the Importance Assigned to SSEC Reform
```{r}
## Running the ordinal logistic regression with pscl package
ordinal_model_imp <- clm(Importance ~ Frame + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D5 + D8, data = x)

## Summarizing the model
summary(ordinal_model_imp)
pR2(ordinal_model_imp)
```

## Rerun the regression as OLS for additional vetting
```{r}
lm_importance<- lm(as.numeric(x$Importance)~x$Frame + as.factor(x$NJ6) + x$NJ7+
x$NJ8+ x$NJ9 +x$NJ10_1 +as.factor(x$NJ11) + x$NJ12 + as.factor(x$D1)+
  as.factor(x$sex) + as.factor(x$agecat)+ x$education + as.factor(x$racethn) +
  x$D5 + as.factor(x$D8) + as.factor(x$vote))


summary(lm_importance)

## OLS confirms nonsignificance of frames, significance of other predictors.

```
## Trump Ordinal Regression Interpreting Incomes as Cutoffs
```{r}
## Defining the cutoff point for incomes above and below 34,00-44,000 USD
## As described by Trump, those above this threshold are eligible to recieve
## Tax cuts. 

x$D5 <- as.numeric(x$D5)
trump <- x |> filter(D5<4 | D5>5) |> mutate(cutoff = ifelse(D5 > 5, 1, 0)) # high values get a 1

trump$cutoff <- as.factor(trump$cutoff)

ordinal_model_t_cutoff <- clm(NJ4 ~ Frame*cutoff + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D8, data = trump)

summary(ordinal_model_t_cutoff)

# Delineating between groups at incomes who are guaranteed to benefit from Trump's
# policy, and those who are guaranteed to not benefit from Trumps policy is
# significant. However, individualist and collectivist frames have no impacts
# on these groups.
```

## Running an Ordinal Model to Predict Support for Trump's SSEC Policy (no cutoff)
```{r}
## Running the ordinal logistic regression with pscl package
ordinal_model_t <- clm(NJ4 ~ Frame + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D5 + D8, data = x)

## Summarizing the model
summary(ordinal_model_t)
pR2(ordinal_model_t)

## Even ignoring the cutoff, people at higher incomes support the policy more than
## People at lower incomes. 
```

## Re-running this model with an interaction term
```{r}
## The goal is to investigate whether income and frame have any interaction
ordinal_model_t_int <- clm(NJ4 ~ Frame*D5 + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D8, data = x)

## Summarizing the model
summary(ordinal_model_t_int)

## Does income influence how people percieve themselves in relation to the policy
## And subsequently influence the significance of the frames?

## The data suggests no - not with these frames.

```

## Rerun Regression as OLS for additional vetting
```{r}
# Trump Policy Support
lm_trump<- lm(as.numeric(x$NJ4)~x$Frame + as.factor(x$NJ6) + x$NJ7+ x$NJ8+ x$NJ9 +x$NJ10_1 +
           as.factor(x$NJ11) + x$NJ12 + as.factor(x$D1)+ as.factor(x$sex) + as.factor(x$agecat)
         + x$education + as.factor(x$racethn) + x$D5 + as.factor(x$D8)
         + as.factor(x$vote))

summary(lm_trump)

## OLS results confirm non-significance of frames, significance of other predictors.
```

## Running an Ordinal Model to Predict Support for Harris' SSEC Policy
```{r}
## Running the model
ordinal_model_h <- clm(NJ5 ~ Frame + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D5 + D8, data = x)

## Summarizing the model
summary(ordinal_model_h)
pR2(ordinal_model_h)



```

## Rerun regression as OLS for additional vetting
```{r}
lm3<- lm(as.numeric(x$NJ5)~x$Frame + as.factor(x$NJ6) + x$NJ7+ x$NJ8+ x$NJ9 +x$NJ10_1 +
           as.factor(x$NJ11) + x$NJ12 + as.factor(x$D1)+ as.factor(x$sex) + as.factor(x$agecat)
         + x$education + as.factor(x$racethn) + x$D5 + as.factor(x$D8)
         + as.factor(x$vote))

summary(lm3)

## OLS confirms non significance of frames, significance of other predictors
```

## Re-running this model with an interaction term
```{r}
## The goal is to investigate whether income and frame have any interaction
ordinal_model_h_int <- clm(NJ5 ~ Frame*D5 + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D8, data = x)

## Summarizing the model
summary(ordinal_model_h_int)

## Does income influence how people percieve themselves in relation to the policy
## And subsequently influence the significance of the frames?

## The data suggests no - not with these frames.

```

## Plotting Regression Outputs

## Confidence Intervals for Ordinal Regression on SSEC Reform Importance by Frame
```{r}

# Step 1: Compute predicted probabilities for Frame
frame_effect <- ggpredict(ordinal_model_imp, terms = "Frame")

# Step 2: Convert to data.frame
frame_effect <- as.data.frame(frame_effect)

# Step 3: Relabel response categories
frame_effect$response.label <- factor(frame_effect$response.level, 
                                      levels = c("1", "2", "3", "4", "5"),
                                      labels = c("Not Important at All", 
                                                 "Mildly Unimportant", 
                                                 "Neither Important nor Unimportant", 
                                                 "Mildly Important", 
                                                 "Important"))

# Step 4: Relabel Frame categories
frame_effect$x <- factor(frame_effect$x,
                         levels = c("NJ3", "NJ1", "NJ2"),
                         labels = c("Control", "Collectivist", "Individualist"))

# Step 5: Plot with proper groupings and restored colors
ggplot(frame_effect, aes(x = x, y = predicted, 
                         ymin = conf.low, ymax = conf.high,
                         color = response.label, 
                         shape = response.label,
                         group = response.label)) +   # <-- this restores proper grouping for lines and legend

  # Reference lines
  geom_hline(yintercept = seq(0, 1, by = 0.1), color = "gray90", linetype = "dotted") +

  # Confidence intervals
  geom_errorbar(linewidth = 1, position = position_dodge(width = 0.4), width = 0.15, na.rm = TRUE) +  

  # Points
  geom_point(size = 3, position = position_dodge(width = 0.4), na.rm = TRUE) +  

  # Color scale
  scale_color_manual(name = "Level of Importance", 
                     values = c("Not Important at All" = "#440154FF", 
                                "Mildly Unimportant" = "#3B528BFF", 
                                "Neither Important nor Unimportant" = "#21908CFF", 
                                "Mildly Important" = "#5DC863FF", 
                                "Important" = "#800000"))+

  # Shape scale
  scale_shape_manual(name = "Level of Importance", 
                     values = c("Not Important at All" = 19, 
                                "Mildly Unimportant" = 19, #from 17
                                "Neither Important nor Unimportant" = 19, #from 15
                                "Mildly Important" = 19, #from 18
                                "Important" = 19)) + #from 16

  # Y-Axis
  scale_y_continuous("Predicted Probability", limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +

  # Labels
  labs(subtitle = str_wrap("How Respondents Ranked SSEC Reform Importance Across Frames"),
       x = "Frame Recieved by Group",
       y = "Predicted Probability of Ranking")+
  
# THEME - Larger, Clean & Top Right Legend
  theme_minimal(base_size = 14) +  
  theme(legend.position = c(2, 1),   # Top Right
        legend.justification = c(1, 1),
        legend.background = element_rect(fill = "white", color = NA),
        legend.key.size = unit(0.8, "cm"),
        legend.text = element_text(size = 11),
        legend.title = element_text(size = 12, face = "bold"),
        panel.grid.major.y = element_line(color = "gray85", linetype = "dotted"),
        axis.text.x = element_text(size = 12))

ggsave("framing_plot_word_ready.png", width = 7, height = 5, dpi = 450)

```


## Trump Policy Facet Graph
```{r}
x$D5 <- as.numeric(x$D5)
trump <- x |> filter(D5<4 | D5>5) |> mutate(Cutoff_Income = ifelse(D5 > 5, 1, 0)) # high values get a 1

trump$Cutoff_Income <- as.factor(trump$Cutoff_Income)

ordinal_model_t_cutoff <- clm(NJ4 ~ Frame*Cutoff_Income + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D8, data = trump)

ordinal_model_t_cutoff_no <- clm(NJ4 ~ Frame + Cutoff_Income + NJ6 + NJ7+ NJ8+ NJ9 +NJ10_1 +
           NJ11 + NJ12 + D1 + sex + agecat+ education + racethn + D8, data = trump)

frame_income_effect_trump <- ggpredict(ordinal_model_t_cutoff, terms = c("Frame", "Cutoff_Income"))
print(frame_income_effect_trump)



# Step 2: Convert to data.frame and rename the interaction variable properly
frame_income_effect_trump <- as.data.frame(frame_income_effect_trump)


# Step 4: Frame relabeling (optional)
frame_income_effect_trump$Frame <- factor(frame_income_effect_trump$x,
                                          levels = c("NJ3", "NJ1", "NJ2"),
                                          labels = c("Control", "Collectivist", "Individualist"))

# Step 5: Response label relabeling
frame_income_effect_trump$response.label <- factor(frame_income_effect_trump$response.level,
                                                   levels = c("1", "2", "3", "4", "5"),
                                                   labels = c("Completely Opposed", 
                                                              "Somewhat Opposed", 
                                                              "Neutral", 
                                                              "Somewhat Supportive", 
                                                              "Completely Supportive"))

#Step 6: Income Group Relabeling
frame_income_effect_trump$Income_group <- factor(frame_income_effect_trump$group,
                                                   levels = c("0", "1"),
                                                   labels = c("Below Income Cutoff", 
                                                              "Above Income Cutoff"))

# Step 6: Now include `Income` inside the ggplot() data

ggplot(frame_income_effect_trump, aes(x = Frame, y = predicted, 
                                      ymin = conf.low, ymax = conf.high,
                                      color = response.label,
                                      shape = response.label,
                                      group = interaction(response.label, Income_group))) +

  geom_hline(yintercept = seq(0, 1, by = 0.1), color = "gray90", linetype = "dotted") +

  geom_errorbar(linewidth = 0.8, 
                 position = position_dodge(width = 0.6), width = 0.15,  # <-- wider dodge
                 na.rm = TRUE) +  

  geom_point(size = 3, 
             position = position_dodge(width = 0.6),   # <-- wider dodge
             na.rm = TRUE) +  

  scale_color_manual(name = "Level of Support",
                     values = c("Completely Opposed" = "#440154FF",
                                "Somewhat Opposed" = "#3B528BFF",
                                "Neutral" = "#21908CFF",
                                "Somewhat Supportive" = "#5DC863FF",
                                "Completely Supportive" = "#800000")) +

  scale_shape_manual(name = "Level of Support",
                     values = c(19, 19, 19, 19, 19)) +  # optional: use different shapes

  scale_y_continuous("Predicted Probability", limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +

  labs(subtitle = "Predicted Support for Social Security Reform by Frame × Income",
       x = "Frame",
       y = "Predicted Probability") +

  facet_wrap(~ Income_group) +    

  theme_minimal(base_size = 14) +  
  theme(legend.position = c(1, 1),
        legend.justification = c(1, 1),
        panel.grid.major.y = element_line(color = "gray85", linetype = "dotted"),
        axis.text.x = element_text(size = 12))

ggsave("framing_interaction_plot_word.png", width = 7, height = 5, dpi = 450)
```

## Plot Ordinal Model Harris Policy
```{r}
# Compute predicted probabilities for Frame
frame_effect_h <- ggpredict(ordinal_model_h, terms = "Frame")


# Step 2: Convert to data.frame
frame_effect_h <- as.data.frame(frame_effect_h)

# Step 3: Relabel response categories
frame_effect_h$response.label <- factor(frame_effect_h$response.level, 
                                      levels = c("1", "2", "3", "4", "5"),
                                      labels = c("Completely Opposed", 
                                                              "Somewhat Opposed", 
                                                              "Neutral", 
                                                              "Somewhat Supportive", 
                                                              "Completely Supportive"))

# Step 4: Relabel Frame categories
frame_effect_h$x <- factor(frame_effect_h$x,
                         levels = c("NJ3", "NJ1", "NJ2"),
                         labels = c("Control", "Collectivist", "Individualist"))

# Step 5: Plot with proper groupings and restored colors
ggplot(frame_effect_h, aes(x = x, y = predicted, 
                         ymin = conf.low, ymax = conf.high,
                         color = response.label, 
                         shape = response.label,
                         group = response.label)) +   # <-- this restores proper grouping for lines and legend

  # Reference lines
  geom_hline(yintercept = seq(0, 1, by = 0.1), color = "gray90", linetype = "dotted") +

  # Confidence intervals
  geom_errorbar(linewidth = 1, position = position_dodge(width = 0.6),width = 0.15, na.rm = TRUE) +  

  # Points
  geom_point(size = 3, position = position_dodge(width = 0.6), na.rm = TRUE) +  

  # Color scale
  scale_color_manual(name = "Level of Support", 
                     values = c("Completely Opposed" = "#440154FF",
                                "Somewhat Opposed" = "#3B528BFF",
                                "Neutral" = "#21908CFF",
                                "Somewhat Supportive" = "#5DC863FF",
                                "Completely Supportive" = "#800000")) +

  # Shape scale
  scale_shape_manual(name = "Level of Support", 
                     values = c("Completely Opposed" = 19, 
                                "Somewhat Opposed" = 19, #from 17
                                "Neutral" = 19, #from 15
                                "Somewhat Supportive" = 19, #from 18
                                "Completely Supportive" = 19)) + #from 16

  # Y-Axis
  scale_y_continuous("Predicted Probability", limits = c(0, 1.0), breaks = seq(0, 1, by = 0.1)) +

  # Labels
  labs(subtitle = str_wrap("How Respondents Felt About Harris' Policy, Across Frames"),
       x = "Frame Recieved by Group",
       y = "Predicted Probability of Support Level")+
  
# THEME - Larger, Clean & Top Right Legend
  theme_minimal(base_size = 14) +  
  theme(legend.position = c(1, 1),   # Top Right
        legend.justification = c(1, 1),
        legend.background = element_rect(fill = "white", color = NA),
        legend.key.size = unit(0.8, "cm"),
        legend.text = element_text(size = 11),
        legend.title = element_text(size = 12, face = "bold"),
        panel.grid.major.y = element_line(color = "gray85", linetype = "dotted"),
        axis.text.x = element_text(size = 12))

ggsave("framing_plot_harris_word.png", width = 7, height = 5, dpi = 450)

```


## Experiment Part 2: Voting Patterns

## Do Voters' Preferences Match their Votes
```{r}
x <- x |> 
  mutate(SupportCategory_4 = case_when(
    NJ4 %in% c(4, 5) ~ "Support",
    NJ4 == 3 ~ "Neutral",
    NJ4 %in% c(1, 2) ~ "Not Support"
  ))

x <- x |> 
  mutate(SupportCategory_5 = case_when(
    NJ5 %in% c(4, 5) ~ "Support",
    NJ5 == 3 ~ "Neutral",
    NJ5 %in% c(1, 2) ~ "Not Support"
  ))

# Calculate the percentage of "Not Support" voters for each candidate
non_support_summary_trump <- x |> 
  group_by(vote) |> 
  summarize(
    Total_Voters = n(),
    Non_Support_Voters = sum(SupportCategory_4 == "Not Support"),
    Percentage_Non_Support = (Non_Support_Voters / Total_Voters) * 100
  )

# Print results
print(non_support_summary_trump)
# 17 percent of Trump supporters do not support Trump's policies, while 22% of
# Harris voters did not support Trump's policies.

# Calculate the percentage of "Not Support" voters for each candidate for Harris Policy
non_support_summary_harris <- x |> 
  group_by(vote) |> 
  summarize(
    Total_Voters = n(),
    Non_Support_Voters = sum(SupportCategory_5 == "Not Support"),
    Percentage_Non_Support = (Non_Support_Voters / Total_Voters) * 100
  )

# Print results
print(non_support_summary_harris)
# 27% of Trump Supporters do not support Harris' policy. Conversely, 18 percent 
# of Harris supporters do not support her own policy. 

# The first table analyzes the percentage of each category of voters who do (not)
# support Trump's policy. 

# The second table analyzes the percentage of each category of voters who do (not)
# Support Harris
```


```{r}
# Calculate the percentage of "Support" voters for each candidate Harris Policy
support_summary_5 <- x %>%
  group_by(vote) %>%
  summarize(
    Total_Voters = n(),
    Support_Voters = sum(SupportCategory_5 == "Support"),
    Percentage_Support = (Support_Voters / Total_Voters) * 100
  )

print(support_summary_5)

# Supporters for Trump Policy
support_summary_4 <- x %>%
  group_by(vote) %>%
  summarize(
    Total_Voters = n(),
    Support_Voters = sum(SupportCategory_4 == "Support"),
    Percentage_Support = (Support_Voters / Total_Voters) * 100
  )

print(support_summary_4)

sum_support_trump <- support_summary_4 |> summarize(Total = sum(Total_Voters), Support = sum(Support_Voters)) |> mutate(Percentage_Total_Support = Support/Total)

sum_support_trump <- sum_support_trump |> mutate(Oppose = Total - Support)
print(sum_support_trump)

sum_support_harris <- support_summary_5 |> summarize(Total = sum(Total_Voters), Support = sum(Support_Voters)) |> mutate(Percentage_Total_Support = Support/Total)

sum_support_harris <- sum_support_harris |> mutate(Oppose = Total - Support)
print(sum_support_harris)
```

## Analyzing whether policy preferences are predictive of voting behavior
```{r}
## Subsetting out non-voters
x2<- x |> filter(vote!=4)

# Fit multinomial logistic regression
multimodel <- multinom(vote ~ NJ4 + NJ5+ NJ6 + NJ7+
+            NJ8+ NJ9 +NJ10_1 +
+            NJ11 + NJ12 + D1+ sex +
+           agecat+ education + as.factor(racethn) + D5
+           + D8, data = x2)

# Extract coefficients and standard errors
summary_model <- summary(multimodel)
coefs <- summary_model$coefficients
std_errors <- summary_model$standard.errors

# Compute Z-values
z_values <- coefs / std_errors

# Compute two-tailed p-values
p_values <- 2 * (1 - pnorm(abs(z_values)))


```

## Creating an interpretable multinomial regression table
```{r}

# Fit multinomial logistic regression
multimodel <- multinom(vote ~ NJ4 + NJ5 + NJ6 + NJ7 + NJ8 + NJ9 + NJ10_1 +
                        NJ11 + NJ12 + D1 + sex + agecat + education + 
                        as.factor(racethn) + D5 + D8, data = x2)

# Convert model output into a structured data frame
results_table <- tidy(multimodel, conf.int = TRUE) %>%
  mutate(Odds_Ratio = exp(estimate)) %>%
  dplyr::select(y.level, term, estimate, std.error, statistic, p.value, conf.low, conf.high)

# Rename columns
results_table <- results_table %>%
  rename(`Outcome` = y.level,
         `Variable` = term,
         `Coef.` = estimate, 
         `Std. Err.` = std.error, 
         `Z` = statistic, 
         `P>|z|` = p.value,
         `[95% Conf. Interval] Lower` = conf.low,
         `[95% Conf. Interval] Upper` = conf.high)

# Format p-values to adjust for small values
results_table <- results_table %>%
  mutate(`P>|z|` = ifelse(`P>|z|` < 0.0001, format(`P>|z|`, scientific = TRUE, digits = 2), 
                          round(`P>|z|`, 4)))

# Format numeric values to 4 decimal places
results_table <- results_table %>%
  mutate(across(where(is.numeric), ~round(., 4)))

# Print table using knitr::kable() for better formatting
kable(results_table, format = "pipe", align = "r", caption = "Multinomial Logistic Regression Results")

```

## Creating Stacked Barplot Dataframes for Visual Aid
```{r}

partisan_trump <- x |> group_by(D8, NJ4) |> summarise(Count = n(), .groups = "drop") |> filter(D8 ==1|D8==2)

## DF for Trump Policy Bar amongst Republicans
R_trump <- partisan_trump |> filter(D8 ==1) |> mutate(Percentage = Count / sum(Count) * 100)

sum(unique(R_trump$Percentage)) ## checking for accuracy

## DF for Trump Policy Bar amongst Democrats
D_trump <- partisan_trump |> filter(D8 ==2) |> mutate(Percentage = Count / sum(Count) * 100)

sum(unique(D_trump$Percentage)) ## checking for accuracy

partisan_harris <- x |> group_by(D8, NJ5) |> summarise(Count = n(), .groups = "drop")

R_harris <- partisan_harris |> filter(D8 ==1) |> mutate(Percentage = Count / sum(Count) * 100)
sum(unique(R_harris$Percentage)) ## checking for accuracy

D_harris <- partisan_harris |> filter(D8 ==2) |> mutate(Percentage = Count / sum(Count) * 100)
sum(unique(D_harris$Percentage)) ## checking for accuracy

all_american_trump <- x |> group_by(NJ4) |> summarise(Count = n(), .groups = "drop") %>%
  mutate(Percentage = Count / sum(Count) * 100) ## Use to plot horizontal barchart

all_american_harris <- x |> group_by(NJ5) |> summarise(Count = n(), .groups = "drop") %>%
  mutate(Percentage = Count / sum(Count) * 100) ## Use to plot horizontal barchart

## If all dataframes are accurate, then the value 100 should be printed 4 times

```

## Reorganizing these Dataframes for Subsequent Plots
```{r}
# Add a new column to specify the group
R_trump <- R_trump |> mutate(Group = "Republicans")
D_trump <- D_trump |> mutate(Group = "Democrats")
all_american_trump <- all_american_trump |> mutate(Group = "All Americans")

# Combine into one dataframe
stacked_data <- bind_rows(R_trump, D_trump, all_american_trump)

# Rename NJ4 for better readability
stacked_data$NJ4 <- factor(stacked_data$NJ4, 
                                      levels = c("1", "2", "3", "4", "5"),
                                      labels = c("Completely Opposed", 
                                                              "Somewhat Opposed", 
                                                              "Neutral", 
                                                              "Somewhat Supportive", 
                                                              "Completely Supportive"))
```

## Plotting Trump Policy
```{r}
ggplot(stacked_data, aes(x = Group, y = Percentage, fill = NJ4)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(Percentage, 0), "%")),
            position = position_stack(vjust = 0.5),  # Center labels within each section
            size = 5,   # Adjust text size
            color = "white",  # White text for better contrast
            fontface = "bold") +  # Make the labels bold+
  # Formatting
  coord_flip() +  # Makes the bar horizontal
  scale_fill_manual(values = c("Completely Opposed" = "#440154FF",
                                "Somewhat Opposed" = "#3B528BFF",
                                "Neutral" = "#21908CFF",
                                "Somewhat Supportive" = "#5DC863FF",
                                "Completely Supportive" = "#800000")) +
  labs(
    title = "American Opinions on Trump's Proposed Social Security Plan \n",
    subtitle = "How do you feel about plans to eliminate the partial income taxation of Social Security benefits for seniors earning more than \n 34,000 USD annually (or 44,000 USD total for married 
couples)? 
\n",
    x = "",
    y = "Percentage",
    fill = "Response"
  ) +
  
  theme_minimal(base_size = 8) +
  theme(
    plot.title = element_text(hjust = 0.5),
    plot.subtitle=element_text(hjust = 0.5),
    panel.grid.major.y = element_blank(),  # Remove y-axis grid lines
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),  # Remove x-axis text (since groups are already labeled)
    axis.ticks.x = element_blank(),
    legend.position = "top"  # Move legend to top
  )

ggsave("descriptive_trump.png", width = 7, height = 5, dpi = 600)
```
## Organizing Data for Harris
```{r}
# Add a new column to specify the group
R_harris <- R_harris |> mutate(Group = "Republicans")
D_harris <- D_harris |> mutate(Group = "Democrats")
all_american_harris <- all_american_harris |> mutate(Group = "All Americans")

# Combine into one dataframe
stacked_data <- bind_rows(R_harris, D_harris, all_american_harris)

# Rename NJ4 for better readability
stacked_data$NJ5 <- factor(stacked_data$NJ5, 
                                      levels = c("1", "2", "3", "4", "5"),
                                      labels = c("Completely Opposed", 
                                                              "Somewhat Opposed", 
                                                              "Neutral", 
                                                              "Somewhat Supportive", 
                                                              "Completely Supportive"))

```

##Plotting Harris
```{r}
ggplot(stacked_data, aes(x = Group, y = Percentage, fill = NJ5)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(Percentage, 0), "%")),
            position = position_stack(vjust = 0.5),  # Center labels within each section
            size = 5,   # Adjust text size
            color = "white",  # White text for better contrast
            fontface = "bold") +  # Make the labels bold+
  # Formatting
  coord_flip() +  # Makes the bar horizontal
  scale_fill_manual(values = c("Completely Opposed" = "#440154FF",
                                "Somewhat Opposed" = "#3B528BFF",
                                "Neutral" = "#21908CFF",
                                "Somewhat Supportive" = "#5DC863FF",
                                "Completely Supportive" = "#800000")) +
  labs(
    title = "American Opinions on Harris's Proposed Social Security Plan \n",
    subtitle = "How do you feel about plans to add a new tier of Social Security tax collection for Americans within the highest income strata? \n",
    x = "",
    y = "Percentage",
    fill = "Response"
  ) +
  
  theme_minimal(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    plot.subtitle=element_text(hjust = 0.5),
    panel.grid.major.y = element_blank(),  # Remove y-axis grid lines
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),  # Remove x-axis text (since groups are already labeled)
    axis.ticks.x = element_blank(),
    legend.position = "top"  # Move legend to top
  )

ggsave("descriptive_harris.png", width = 7, height = 5, dpi = 600)
```

## Transferring Regression Tables to Word

## Ordinal Regression 1: Importance
```{r}

coef(summary(ordinal_model_imp))
coef_table <- as.data.frame(coef(summary(ordinal_model_imp)))
print(coef_table)

colnames(coef_table) <- c("Estimate", "Std. Error", "z value", "p value")



coef_table <- coef_table %>%
  mutate(`p value` = ifelse(`p value` < 0.0001, format(`p value`, scientific = TRUE, digits = 2), 
                            round(`p value`, 4))) 

# Convert to flextable
ft <- flextable(coef_table) %>%
  colformat_num(j = c("Estimate", "Std. Error", "z value"), digits = 4) %>%  # Round other numbers
  colformat_char(j = "p value") %>%  # Ensure p-values are treated as text
  autofit()

# Save as a Word document
save_as_docx(ft, path = "ordinal_regression_results_1.docx")

```

##Trump Ordinal Model
```{r}

coef(summary(ordinal_model_t_cutoff_no))
coef_table <- as.data.frame(coef(summary(ordinal_model_t_cutoff_no)))
print(coef_table)

colnames(coef_table) <- c("Estimate", "Std. Error", "z value", "p value")




coef_table <- coef_table %>%
  mutate(`p value` = ifelse(`p value` < 0.0001, format(`p value`, scientific = TRUE, digits = 2), 
                            round(`p value`, 4))) 

# Convert to flextable
ft <- flextable(coef_table) %>%
  colformat_num(j = c("Estimate", "Std. Error", "z value"), digits = 4) %>%  # Round other numbers
  colformat_char(j = "p value") %>%  # Ensure p-values are treated as text
  autofit()

# Save as a Word document
save_as_docx(ft, path = "ordinal_regression_results_t.docx")
```

## Harris Ordinal Model
```{r}

coef(summary(ordinal_model_h))
coef_table <- as.data.frame(coef(summary(ordinal_model_h)))
print(coef_table)

colnames(coef_table) <- c("Estimate", "Std. Error", "z value", "p value")




coef_table <- coef_table %>%
  mutate(`p value` = ifelse(`p value` < 0.0001, format(`p value`, scientific = TRUE, digits = 2), 
                            round(`p value`, 4))) 

# Convert to flextable
ft <- flextable(coef_table) %>%
  colformat_num(j = c("Estimate", "Std. Error", "z value"), digits = 4) %>%  # Round other numbers
  colformat_char(j = "p value") %>%  # Ensure p-values are treated as text
  autofit()

# Save as a Word document
save_as_docx(ft, path = "ordinal_regression_results_h.docx")

summary(ordinal_model_h)
```

## Exporting multinomial regression to word
```{r}

# Create a flextable for Word export
flex_table <- flextable(results_table) %>%
  theme_vanilla() %>%  # Clean professional styling
  autofit()

# Save table to a Word document
doc <- read_docx() %>%  # Create a new Word document
  body_add_flextable(flex_table) %>%
  body_add_par(" ")  # Add space after the table

print(doc, target = "Multinomial_Regression_Results.docx")

# Show the table in RStudio
flex_table
```

